Nengo: A Python tool for building large-scale functional brain models

### 2013-09-27 nengo.tex
new benchmark figure

Some stuff about benchmarking

\begin{figure}
\begin{center}
  \includegraphics[width=0.5\textwidth]{benchmark}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:benchmarks} Figure \arabic{figure}.}{
   Benchmarks}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.5\textwidth]{ocl_vs_ref}
\end{center}
 \textbf{
     \refstepcounter{figure}\label{fig:ocl_vs_ref}
     Figure \arabic{figure}.}{
     Five-hundred-dimensional circular convolution networks were some of the most
     computationally demanding elements of the Spaun cognitive architecture.
     Simulations of circular convolution networks of various sizes illustrate the speed of our re-engineered simulators.
     A straightforward reference implementation in Python is sufficient for small networks,
     while for larger ones the new OpenCL-powered simulator runs up to 200$\times$ faster,
     In particular the Radeon 7970 GPU can simulate 500-dimensional convolution networks faster than real time (0.95 seconds for a 1-second simulation).
     Also, although both are multithreaded, our new implementation delivers better CPU performance than the previous JavaNengo implementation.
     }
\end{figure}
